---
title: "ToothGrowth data  in the R datasets package"
author: "Suresh Babu Kumpati"
date: "November 22, 2015"
output: pdf_document
---

Statistical Inference Course Project Part 2

# Description

Now in the second portion of the class, we're going to analyze the ToothGrowth data in the R datasets package. 
Load the ToothGrowth data and perform some basic exploratory data analyses 
Provide a basic summary of the data.
Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)
State your conclusions and the assumptions needed for your conclusions. 
Some criteria that you will be evaluated on
Did you  perform an exploratory data analysis of at least a single plot or table highlighting basic features of the data?
Did the student perform some relevant confidence intervals and/or tests?
Were the results of the tests and/or intervals interpreted in the context of the problem correctly? 
Did the student describe the assumptions needed for their conclusions?

## Question 1
#Load the ToothGrowth data and perform some basic exploratory data analyses

```{r}
library(ggplot2)
library(datasets)
data(ToothGrowth)
str(ToothGrowth)
head(ToothGrowth)


plot <- ggplot(ToothGrowth, 
               aes(x=factor(dose),y=len,fill=factor(dose)))
plot + geom_boxplot(notch=F) + facet_grid(.~supp) +
     scale_x_discrete("Dosage (Milligram)") +   
     scale_y_continuous("Length of Teeth") +  
     ggtitle("Exploratory Data Analyses")
```
## Question 2
#Provide a basic summary of the data.

```{r}
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
summary(ToothGrowth)
```
##     len        supp     dose   
## Min.   : 4.20   OJ:30   0.5:20  
## 1st Qu.:13.07   VC:30   1  :20  
## Median :19.25           2  :20  
## Mean   :18.81                   
## 3rd Qu.:25.27                   
## Max.   :33.90   
```{r}
table(ToothGrowth$supp, ToothGrowth$dose)
```
##    0.5  1  2
##  OJ  10 10 10
##  VC  10 10 10

# Question 3
## Use confidence intervals and hypothesis tests to compare tooth growth by supp and dose. (Use the techniques from class even if there’s other approaches worth considering)

```{r}
supp.t1 <- t.test(len~supp, paired=F, var.equal=T, data=ToothGrowth)
supp.t2 <- t.test(len~supp, paired=F, var.equal=F, data=ToothGrowth)
supp.result <- data.frame("p-value"=c(supp.t1$p.value, supp.t2$p.value),
                          "Conf-Low"=c(supp.t1$conf[1],supp.t2$conf[1]),
                          "Conf-High"=c(supp.t1$conf[2],supp.t2$conf[2]),
                          row.names=c("Equal Var","Unequal Var"))
supp.result
```
##              p.value   Conf.Low Conf.High
## Equal Var   0.06039337 -0.1670064  7.567006
## Unequal Var 0.06063451 -0.1710156  7.571016

# Question 4
## State your conclusions and the assumptions needed for your conclusions.

Based on the sample data provided:

1- The 2mg dose has larger impact on tooth growth than 1mg and 0.5mg, while 1mg dose has more impact than 0.5mg dose. So there is a different in the growth of the tooth while the doses are larger.

2- There is no doubt that orange juice and vitamin C have obvious different impact on tooth growth.


